Predicting Evaluation Prices of Danish Real Estate Property

### 2019-08-29 Opsætningexam/DraftExam.tex
de

Figure 1 shows the average square meter price valuation of active offers per municipality in Denmark. The maximum square meter price being approximately 8 times higher in the municipality of Gentofte, than Lolland, the municipality with the lowest average square meter price valuations. A tendency visualised in the figure, is that average square meter price valuations are higher in highly populated municipalities and in suburban areas surrounding Copenhagen. \newline

The valuations included in the research are collected from one of Denmarks largest online real estate websites named Boliga.dk. The Boliga data contains approximately 66,000 active offerings with valuations ranging from DKK 15,000 to DKK 85 million. This research paper intends to use machine learning to analyse real estate price valuations and which geographical and sociodemographic criteria affect valuations. Our research question is as follows: 
\begin{center}
 \textit{How can geographic and sociodemographic features be utilised to predict real estate property valuations in Denmark?}
\end{center}
This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the dataset. Also, a section regarding the choice and optimisation of machine learning models is included, where the intention is to provide insights on our progress of finding the optimal model. As a result, the best performing model is chosen with a discussion of its usability.

@@

In considering the legal ramifications of our research and to make sure we adhere to the seven principles of GDPR, and other appropriate legislation and legal contracts, we consulted the general guidelines introduced by the Consumer Data Research Center. In particular we noted that we are justified to collect and use the data on the lawful basis of legitimate interests. Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}. In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function. This causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page (see Jupyter). 

@@

\paragraph{\href{https://www.hvorlangterder.dk}{hvorlangterder.dk}\newline}
\href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to everyday commodities such as supermarkets, hospitals and schools.   

@@

\subsection{Merging Data}
Pandas objects can be combined in different ways according to the nature of the features in the dataset. Relational database style operations are based on linking keys together, thereby maintaining the relationship between the combined datasets\footnote{McKinney, W. (2018). \textit{Data Wrangling: Join, Combine and Reshape}. p. 231 }.

The data collection and scraping process provided a total of 15 Datasets from Boliga, hvorlangterder, DAWA, the Danish Police, Social- \& Indenrigsministeriet and Danmarks Statistik. This section will describe how each dataset was merged, using pandas relational database styled merge and join operations.

@@

\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.4]{predictactual.png}
%\source{}
\end{figure}
We are somewhat satisfied with the average performance of the model. With an MSE of approximately $55\cdot10^{10}$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data. Therefore, we chose this model as the final model from which we will conduct the rest of the analysis with. In the following section further assessment of the model will be conducted  \newline

\paragraph{Learning Curve\newline}
We examine the learning curve of the model to assert whether the model suffers from immediate over- or underfitting problems and whether these would be remedied by collecting more data\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p. 196}
The following plot illustrates the learning curve of our model:
\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.6]{Learncurvridge.png}
%\source{}
\end{figure}
The plotted curves represent the average performance of the validation- and training sets, while the width of the plotted curves expresses the 95\%-confidence interval of the performance.  
The performance on the validation set is very inconsistent and varies a lot. Nonetheless, it seems as if the gap is decreasing between the performances of the training- and validation sets as the sample size increases. 
At around 33,000 observations the validation curve drastically decreases and both curves flatten out. Though the confidence interval of the validation performance is still noteworthy, it also improves dramatically when the sample gets sufficiently high. Just before 40,000 observations, the confidence interval of the validation curve actually drops below the train curve, which should not be possible. We have not found a meaningful explanation aside from noise or chance \footnote{\href{https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html}{jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html}} 
All in all, the learning curve would indicate that the performance of the model will not benefit from additional training data.

\paragraph{Validation Curve\newline}
We examine the validation curve of the model to see whether we have found a good bias-variance trade-off with our optimised hyperparameter. We plot the average train and cross-validation performance for different values of $\lambda$: 
\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.6]{ValCurveRidge3deg.png}
%\source{}
\end{figure}
The dotted line approximately represents the optimised value of $\lambda$ from our previously conducted k-fold cross-validation. 
The curves suggest that we have found the optimal degree of regularisation with our hyperparameter. Had we chosen a smaller value of $\lambda$, the model would have had too high variance and thus been overfit. This is deduced by how poorly the validation predictions performs at smaller $\lambda$, as opposed to the training performance. On the contrary, had we chosen a greater value of $\lambda$, the model would have been too biased. This is illustrated by how poorly the training data, as well as the validation data, performs at higher values of $\lambda$ . In that case, we would have underfitted our model. 
Nonetheless, it is apparent that our model performs better on the training data, which indicates that it retains a degree of overfitting. For the abovementioned reasons, it would not be meaningful to minimise this performance gab by adjusting the hyperparameter. Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, this would not seem to effect the variance. Lastly, as overfitting is often caused by a sizeable number of features, omission would be a reasonable mean. As we have already conducted feature selection on the basis of correlations, we did not find a feasible way to conduct further selection without omitting theoretically warranted features. This could be a subject for further studies, to investigate whether this could improve the performance and evaluation of the model. \newline
To sum up it would seem that we have found the hyperparameter which yields the optimal bias-variance trade-off. We can thus conclude that we have optimised our model under the given resources.

@@

\section{Conclusion}
In this research paper we have used machine learning to train a model to predict valuation prices of real estate in Denmark. The model train on sociodemographic and geographical data. \newline We did this by scraping Boliga.dk for all of their listed housing and combining this with municipal data on income, education, schools and urbanisation. Additionally, we also scraped data from hvorlangterder.dk which calculates the distance from an address, to different every-day commodities such as hospitals, schools and shopping. 
We have explained how we carried out our gathering of data, how we have structured the data and how we cleaned it. \newline
We performed descriptive statistics to gain a better acquaintance with the data. 
We conducted feature selection by assessing the correlation between the different features and the target variable, which in our research has been the valuation price. 
We trained both a LASSO- and a RIDGE regression model and compared their performances with the performance of a standard linear regression. Through k-fold cross-validation, we estimated the optimised hyperparameters for both regularisation models. We found that the RIDGE regression with three polynomial features performed best, at predicting out-of-sample data with the performance measure being the smallest mean square error. When predicting the test data the model had a MSE of 5.566e+10 with a optimised hyperparameter $\lambda$=432.88 which we found to be a decent performance. 
We have assessed the final model and examined to which degree we have managed to find a good bias-variance trade-off for our model and concluded that our model suffers from a degree of overfitting. This was done by examining the validation- and learning curve of our final model. Additionally we addressed possibilities of further optimising the model.  \newline
Finally, we have discussed the results of our analysis. We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement. In conclusion, we found that sociodemographical and geographical features can be utilised to a satisfactory degree in predicting real estate valuations in Denmark

\newpage
\section{Litterature}
\ Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press 2017 \newline

Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}, $2^{nd}$editon, Packt Publishing 2017. \newline

Varian. Hal R. \textit{Big data: New tricks for econometrics}. Journal of Economic Perspectives, 28(2):3–28, 2014. \newline

Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \newline\href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020} [Accessed on 25/08/2019]\newline

European Commission (2018). \textit{Ethics in Social Sciences and the Humanities} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities} [Accessed on 25/08/2019] \newline

Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}. Encounter, March 1969, pp. 52-56 [Online]: \href{http://www.unz.com/print/Encounter-1969mar-00052}{http://www.unz.com/print/Encounter-1969mar-00052} [Accessed on 25/08/2019]\newline

Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}. Science, November 1999: Vol. 286, Issue 5444, pp. 1475 [Online]: \href{https://science.sciencemag.org/content/286/5444/1475.full}{https://science.sciencemag.org/content/286/5444/1475.full} [Accessed on 25/08/2019] DOI: 10.1126/science.286.5444.1475 \newline

Salganik, Matthew J. (2018) \textit{Bit by Bit - Social research in the digital age.} Princeton, NJ: Princeton University Press.\newline

Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic Oath, says academic.} The Guardian [Online]: \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry} [Accessed on 25/08/2019]\newline

Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]: \href{https://www.vox.com/2018/4/10/17207394/cambridge-analytica-facebook-zuckerberg-trump-privacy-scandal} [Accessed on 26/08/2019] \newline

Boligagruppen.dk (2019) \textit{Om boliga gruppen} [Online]: \href{https://www.boligagruppen.dk}{www.boligagruppen.dk}: [Accessed on 27/08/2019] \newline

Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism. Global Investigative Journalism Network.} [Online]: \href{https://gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}{gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}: [Accessed on 27/08/2019] \newline

McKinney, W. (2018). 'Data Wrangling: Join, Combine and Reshape'. In W. McKinney, \textit{Python for Data Analysis}. Sebastopol: O'Reilly Media Inc. \newline

Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al. (eds) \textit{The Economics of Artificial Intelligence: An Agenda} (2019). Chicago: University of Chicago Press. \newline

Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}. Science, vol. 346, November. \newline

Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together}. PS: Political Science \& Politics, vol. 48, January: 80-83. \newline

Lazer, David and Jason Radford (2017) \textit{Data ex Machina. Introduction to Big Data. Annual Review of Sociology}, vol. 43, August. \newline

Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}. Journal of Economic Perspectives, vol. 31 (2): 87-106. \newline

Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}. Wired, 16-07 [Online] \href{https://www.wired.com/2008/06/pb-theory/}{www.wired.com/2008/06/pb-theory/} [Accessed on 27/08/2019]\newline

Peckov, Aleksandar. (2012)  \textit{A Machine Learning Approach To Polynomial Regression}. Available at \href{http://kt.ijs.si/theses/phd_aleksandar_peckov.pdf}{kt.ijs.si/theses/phd\_aleksandar\_peckov.pdf}. Doctoral Dissertation. Jozef Stefan International Postgraduate School. Ljubljana, Slovenia, October 2012. [Accessed on 29/08/2019]

(https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html). [Accessed on 29/08/2019]\newline

Gareth, J., Witten, D., Tibshirani, R., \& Hastie, T. (2017). Linear Model Selection and Regularization. In J. Gareth, D. Witten, R. Tibshirani, \& T. Hastie, \textit{An Introduction to Statistical Learning} (pp. 205-262). New York City: Springer.

https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979 [Accessed 27/08/2019]\newline

https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741 [Accessed 27/08/2019]\newline
\newpage
\section{Appendix}
\subsubsection{}
Excluded Features:\newline
municipality, lotSize, unemployment, Total\_reported\_crime, Socioeconomic\_index, expenses\_per\_school\_student, expenses\_sport\_and\_other\_cultural\_activities, forest\_distance, coast\_distance, isForeclosure, owners\_expense
\subsubsection{}
The model used for prediction: 
$$ \hat{Y_i}=\hat{\beta_0}+\sum_{i=1}^p\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^pX_j^{d_i,j}
\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 6-9}$$
\small{$p$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
$$\textbf{X}_j=\begin{bmatrix}
           basementSize \\
           buildYear \\
           rooms \\
           size \\
           primary\_school\_educ \\
           high\_school\_educ \\
           vocational\_educ \\
           SHE \\
           MHE \\
           bachelors\_degree \\
           LHE \\
           avg\_municipal\_income\_2017 \\
           Population\_in\_urban\_development \\
           Socioeconomic\_index \\
           lake\_distance\\
           doctor\_distance \\
           supermarket\_distance \\
           school\_distance \\
           daycare\_distance \\
           hospital\_distance \\
           train\_distance \\
           pharmacy\_distance \\
           library\_distance \\
         \end{bmatrix}$$
\newpage
\subsubsection{}  
\begin{tabular}{|c|c|c|}
\hline 
\textbf{Feature} & \textbf{Description} & \textbf{Dropped} \\ 
\hline 
agentDisplayName & Real estate Agent Name & True \\ 
\hline 
agentRegId & Real-estate Agent ID & True \\ 
\hline 
area & Area of country (11 areas) & True \\ 
\hline 
basementSize & Square meters of basement & False \\ 
\hline 
buildYear & Year of house built & False \\ 
\hline 
city & City Name & False \\ 
\hline 
createdDate & Day of offer creation & True \\ 
\hline 
daysForSale & Scraping date - createdDate & False \\ 
\hline 
domainId & Description unknown & True \\ 
\hline 
energyClass & Energy scale - not sufficiently formated & True \\ 
\hline 
exp & Property expenses & False \\ 
\hline 
floor & Entrance floor & False \\ 
\hline 
groupKey & Key for same buildings & True \\ 
\hline 
guid & Link & True \\ 
\hline 
id & Unique identifier & True \\ 
\hline 
images & Image format dictionary & True \\ 
\hline 
inWatchlist & In profile's watchlist & True \\ 
\hline 
isActive & If the offer is active on webpage (all are active)
 & True \\ 
\hline 
isForeclosure & The house is being foreclosed & True \\ 
\hline 
isPremiumAgent & An agent ranking & True \\ 
\hline 
latitude & Latitude of address & False \\ 
\hline 
longitude & Longitude of adress & False \\ 
\hline 
lotSize & Size of total property & False \\ 
\hline 
municipality & Municipality code & False \\ 
\hline 
net & Description unknown & True \\ 
\hline 
openHouse & Boolean. True if future open house date exists & True \\ 
\hline 
price & Total price (Target) & False \\ 
\hline 
priceChangePercentTotal & Price change since first valuation & True \\ 
\hline 
propertyType & Property type category & False \\ 
\hline 
rooms & No. of rooms & False \\ 
\hline 
selfsale & Bool if property sold without agen & True \\ 
\hline 
size & Size of residential property & False \\ 
\hline 
squaremeterPrice & Price/size & True \\ 
\hline 
street & Street name & True \\ 
\hline 
views & No. of views on website & True \\ 
\hline 
zipCode & Zipcode (Post nr.) & True \\ 
\hline 
\end{tabular}

>>>>

Figure 1 shows the average square meter price valuation of active offers per municipality in Denmark. The maximum square meter price being approximately 8 times higher in the municipality of Gentofte, than Lolland, the municipality with the lowest average square meter price valuations. A tendency visualised in the figure, is that average square meter price valuations are higher in highly populated municipalities and in suburban areas surrounding Copenhagen. \newline
The valuations included in the research are collected from one of Denmarks largest online real estate websites named Boliga.dk. The Boliga data contains approximately 66,000 active offerings with valuations ranging from DKK 15,000 to DKK 85 million. This research paper intends to use machine learning to analyse real estate price valuations and which geographical and sociodemographic criteria affect valuations. Our research question is as follows: 
\begin{center}
 \textit{How can geographic and sociodemographic features be utilised to predict real estate property valuations in Denmark?}
\end{center}
This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the dataset. Also, a section regarding the choice and optimisation of machine learning models is included, where the intention is to provide insights on our progress of finding the optimal model. As a result, the best performing model is chosen with a discussion of its usability.

@@

In considering the legal ramifications of our research and to make sure we adhere to the seven principles of GDPR, and other appropriate legislation and legal contracts, we consulted the general guidelines introduced by the Consumer Data Research Center. In particular we noted that we are justified to collect and use the data on the lawful basis of legitimate interests. Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}. In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function. This causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page. See attached Jupyter notebooks. 

@@

\paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk} returns distances from a given address, to everyday commodities such as supermarkets, hospitals and schools.   

@@

\subsection{Merging Data}
Pandas objects can be combined in different ways according to the nature of the features in the dataset. Relational database style operations are based on linking keys together, thereby maintaining the relationship between the combined datasets\footnote{McKinney, W. (2018). \textit{Data Wrangling: Join, Combine and Reshape}. p. 231 }.\newline
The data collection and scraping process provided a total of 15 Datasets from Boliga, hvorlangterder, DAWA, the Danish Police, Social- \& Indenrigsministeriet and Danmarks Statistik. This section will describe how each dataset was merged, using pandas relational database styled merge and join operations.

@@

\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.4]{predictactual.png}
%\source{}
\end{figure}
We are somewhat satisfied with the average performance of the model. With an MSE of approximately $55\cdot10^{10}$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data. Therefore, we chose this model as the final model from which we will conduct the rest of the analysis with. In the following section further assessment of the model will be conducted.

\subsection{Learning Curve}
We examine the learning curve of the model to assert whether the model suffers from immediate over- or underfitting problems and whether these would be remedied by collecting more data\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p. 196}
The following plot illustrates the learning curve of our model:
\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.6]{Learncurvridge.png}
%\source{}
\end{figure}
The plotted curves represent the average performance of the validation- and training sets, while the width of the plotted curves expresses the 95\%-confidence interval of the performance.  
The performance on the validation set is very inconsistent and varies a lot. Nonetheless, it seems as if the gap is decreasing between the performances of the training- and validation sets as the sample size increases. 
At around 33,000 observations the validation curve drastically decreases and both curves flatten out. Though the confidence interval of the validation performance is still noteworthy, it also improves dramatically when the sample gets sufficiently high. Just before 40,000 observations, the confidence interval of the validation curve actually drops below the train curve, which should not be possible. We have not found a meaningful explanation aside from noise or chance \footnote{\href{https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html?fbclid=IwAR22jhu2nrTY3eJME4VTuTSLXNKqNMmPzlwU4-IJ8VvEMIsLy05-IqgQdsI}{Van der Plas, Jake. (2016)}} 
All in all, the learning curve would indicate that the performance of the model will not benefit from additional training data.

\subsection{Validation Curve}
We examine the validation curve of the model to see whether we have found a good bias-variance trade-off with our optimised hyperparameter. We plot the average train and cross-validation performance for different values of $\lambda$: 
\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.6]{ValCurveRidge3deg.png}
%\source{}
\end{figure}
The dotted line approximately represents the optimised value of $\lambda$ from our previously conducted k-fold cross-validation. 
The curves suggest that we have found the optimal degree of regularisation with our hyperparameter. Had we chosen a smaller value of $\lambda$, the model would have had too high variance and thus been overfit. This is deduced by how poorly the validation predictions performs at smaller $\lambda$, as opposed to the training performance. On the contrary, had we chosen a greater value of $\lambda$, the model would have been too biased. This is illustrated by how poorly the training data, as well as the validation data, performs at higher values of $\lambda$ . In that case, we would have underfitted our model. 
Nonetheless, it is apparent that our model performs better on the training data, which indicates that it retains a degree of overfitting. For the abovementioned reasons, it would not be meaningful to minimise this performance gab by adjusting the hyperparameter. Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, this would not seem to effect the variance. Lastly, as overfitting is often caused by a sizeable number of features, omission would be a reasonable mean. As we have already conducted feature selection on the basis of correlations, we did not find a feasible way to conduct further selection without omitting theoretically warranted features. This could be a subject for further studies, to investigate whether this could improve the performance and evaluation of the model. \newline
To sum up it would seem that we have found the hyperparameter which yields the optimal bias-variance trade-off. We can thus conclude that we have optimised our model under the given resources.

@@

\section{Conclusion}
In this research paper we have used machine learning to train a model to predict valuation prices of real estate in Denmark. The model train on sociodemographic and geographical data. \newline We did this by scraping Boliga.dk for all of their listed housing and combining this with municipal data on income, education, schools and urbanisation. Additionally, we also scraped data from hvorlangterder.dk which calculates the distance from an address, to different every-day commodities such as hospitals, schools and shopping. 
We have explained how we carried out our gathering of data, how we have structured the data and how we cleaned it. \newline
We performed descriptive statistics to gain a better acquaintance with the data. 
We conducted feature selection by assessing the correlation between the different features and the target variable, which in our research has been the valuation price. 
We trained both a LASSO- and a RIDGE regression model and compared their performances with the performance of a standard linear regression. Through k-fold cross-validation, we estimated the optimised hyperparameters for both regularisation models. We found that the RIDGE regression with three polynomial features performed best, at predicting out-of-sample data with the performance measure being the smallest mean square error. When predicting the test data the model had a MSE of 5.566e+10 with a optimised hyperparameter $\lambda$=432.88 which we found to be a decent performance. 
We have assessed the final model and examined to which degree we have managed to find a good bias-variance trade-off for our model and concluded that our model suffers from a degree of overfitting. This was done by examining the validation- and learning curve of our final model. Additionally we addressed possibilities of further optimising the model.  \newline
Finally, we have discussed the results of our analysis. We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement. \newline In conclusion, we found that sociodemographical and geographical features can be utilised to a satisfactory degree in predicting real estate valuations in Denmark

\newpage
\section{Litterature}
Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete.} Wired, 16-07 [Online] \url{www.wired.com/2008/06/pb-theory/} [Accessed on 27/08/2019]

Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al. (eds) \textit{The Economics of Artificial Intelligence: An Agenda} (2019) Chicago: University of Chicago Press.

Consumer Data Research Center, UK [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \href{https://www.cdrc.ac.uk/wp-content/uploads/2018/05/6-GDPR-and-social-science-research-full-document-1.pdf}{https://www.cdrc.ac.uk} [Accessed on 27/08/2019]

Boligagruppen.dk (2019) \textit{Om boliga gruppen} [Online]: \url{www.boligagruppen.dk}: [Accessed on 27/08/2019]

DST (2019) \url{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979} [Accessed 27/08/2019]

DST (2019) \url{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741} [Accessed 27/08/2019]

Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data.} Science, vol. 346, November.

European Commission (2018) \textit{Ethics in Social Sciences and the Humanities}[Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-sciencehumanities_en.pdf}{https://ec.europa.eu/}[Accessed on 25/08/2019]

Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; (2017) \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press

Gareth, J., Witten, D., Tibshirani, R., \& Hastie, T. (2017) \textit{Linear Model Selection and Regularization.} In J. Gareth, D.Witten, R. Tibshirani, \& T. Hastie, \textit{An Introduction to Statistical Learning}(pp. 205-262). New York City: Springer.

Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together.} PS: Political Science \& Politics, vol. 48, January: 80-83.

Lazer, David and Jason Radford (2017) D\textit{ata ex Machina. Introduction to Big Data}. Annual Review of Sociology, vol. 43, August.

McKinney, W. (2018) ’Data Wrangling: Join, Combine and Reshape’. In W. McKinney, \textit{Python for Data Analysis}. Sebastopol: O’Reilly Media Inc.

Mullainathan, Sendhil, and Jann Spiess (2017)\textit{ Machine Learning: An Applied Econometric Approach.} Journal of Economic Perspectives, vol. 31 (2): 87-106.

Peckov, Aleksandar. (2012) \textit{A Machine Learning Approach To Polynomial Regression.} Available at \url{kt.ijs.si/theses/phd_aleksandar_peckov.pdf} Doctoral Dissertation. Jozef Stefan International Postgraduate School. Ljubljana, Slovenia, October 2012. [Accessed on 29/08/2019]

Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}. Encounter, March 1969, pp. 52-56 [Online]: \href{http://www.unz.com/print/Encounter-1969mar-00052}{unz.com} [Accessed on 25/08/2019]

Rashka, Sebastian; Mirjalli, Vahid; (2017) \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} 2ndediton, Packt Publishing

Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}. Science, November 1999: Vol. 286, Issue 5444, pp. 1475 [Online]: \url{https://science.sciencemag.org/content/286/5444/1475.full} [Accessed on 25/08/2019] DOI: 10.1126/science.286.5444.1475

Salganik, Matthew J. (2018) \textit{Bit by Bit - Social research in the digital age}. Princeton, NJ: Princeton University Press.

Sample, Ian (2019, Fri 16 Aug 2019) \textit{Maths and tech specialists need Hippocratic oath, says academic.} The Guardian [Online]: \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry}{www.theguardian.com} [Accessed on 25/08/2019]

Shiab, Nael (2015) O\textit{n the Ethics of Web Scraping and Data Journalism}. Global Investigative Journalism Network. [Online]: \href{gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}{gijn.org}: [Accessed on 27/08/2019]
Varian. Hal R. \textit{Big data: New tricks for econometrics}. Journal of Economic Perspectives, 28(2):3–28, 2014.

Van der Plas, Jake. (2016)\textit{Python Data Science Handbook} available at: \href{https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html?fbclid=IwAR22jhu2nrTY3eJME4VTuTSLXNKqNMmPzlwU4-IJ8VvEMIsLy05-IqgQdsI}{GitHub} [Accessed on 29/08/2019]

Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]: \href{https://www.vox.com/2018/4/10/17207394/cambridge-analytica-facebook-zuckerberg-trump-privacy-scandal}{vox.com} [Accessed on 26/08/2019]

\newpage
\section{Appendix}
\subsubsection{}
Excluded Features:\newline
municipality, lotSize, unemployment, Total\_reported\_crime, Socioeconomic\_index, expenses\_per\_school\_student, expenses\_sport\_and\_other\_cultural\_activities, forest\_distance, coast\_distance, isForeclosure, owners\_expense
\subsubsection{}
The model used for prediction: 
$$ \hat{Y_i}=\hat{\beta_0}+\sum_{i=1}^p\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^pX_j^{d_i,j}
\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 6-9}$$
\small{$p$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
$$\textbf{X}_j=\begin{bmatrix}
           basementSize \\
           buildYear \\
           rooms \\
           size \\
           primary\_school\_educ \\
           high\_school\_educ \\
           vocational\_educ \\
           SHE \\
           MHE \\
           bachelors\_degree \\
           LHE \\
           avg\_municipal\_income\_2017 \\
           Population\_in\_urban\_development \\
           Socioeconomic\_index \\
           lake\_distance\\
           doctor\_distance \\
           supermarket\_distance \\
           school\_distance \\
           daycare\_distance \\
           hospital\_distance \\
           train\_distance \\
           pharmacy\_distance \\
           library\_distance \\
         \end{bmatrix}$$
\newpage
\subsubsection{}  
\begin{tabular}{|c|c|c|}
\hline 
\textbf{Feature} & \textbf{Description} & \textbf{Dropped} \\ 
\hline 
agentDisplayName & Real estate Agent Name & True \\ 
\hline 
agentRegId & Real-estate Agent ID & True \\ 
\hline 
area & Area of country (11 areas) & True \\ 
\hline 
basementSize & Square meters of basement & False \\ 
\hline 
buildYear & Year of house built & False \\ 
\hline 
city & City Name & False \\ 
\hline 
createdDate & Day of offer creation & True \\ 
\hline 
daysForSale & Scraping date - createdDate & False \\ 
\hline 
domainId & Description unknown & True \\ 
\hline 
energyClass & Energy scale - not sufficiently formated & True \\ 
\hline 
exp & Property expenses & False \\ 
\hline 
floor & Entrance floor & False \\ 
\hline 
groupKey & Key for same buildings & True \\ 
\hline 
guid & Link & True \\ 
\hline 
id & Unique identifier & True \\ 
\hline 
images & Image format dictionary & True \\ 
\hline 
inWatchlist & In profile's watchlist & True \\ 
\hline 
isActive & If the offer is active on webpage (all are active)
 & True \\ 
\hline 
isForeclosure & The house is being foreclosed & True \\ 
\hline 
isPremiumAgent & An agent ranking & True \\ 
\hline 
latitude & Latitude of address & False \\ 
\hline 
longitude & Longitude of adress & False \\ 
\hline 
lotSize & Size of total property & False \\ 
\hline 
municipality & Municipality code & False \\ 
\hline 
net & Description unknown & True \\ 
\hline 
openHouse & Boolean. True if future open house date exists & True \\ 
\hline 
price & Total price (Target) & False \\ 
\hline 
priceChangePercentTotal & Price change since first valuation & True \\ 
\hline 
propertyType & Property type category & False \\ 
\hline 
rooms & No. of rooms & False \\ 
\hline 
selfsale & Bool if property sold without agen & True \\ 
\hline 
size & Size of residential property & False \\ 
\hline 
squaremeterPrice & Price/size & True \\ 
\hline 
street & Street name & True \\ 
\hline 
views & No. of views on website & True \\ 
\hline 
zipCode & Zipcode (Post nr.) & True \\ 
\hline 
\end{tabular}
